Optimal (Multiway) Spatial Joins

### 2024-06-04 msj.tex
yufei

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(\bm{t}) = \contained_{R_{k-2}}(h^*)$. We can then derive 
\myeqn{
    \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)|
    \le
    \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})|
    \leq \out \nn
} where the last inequality is due to Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

Now, we explain the mapping. Consider an arbitrary $h^* \in H^*$. Recall that $h^*$ is the minimal segment of some segment $h' \in H'$. Specifically, if $h' = [x_1,x_2]\times y$, then $h^* = [x_1,\minleft(h')]\times y$. By the definition of $\minleft(h')$ in \eqref{eqn:hv:type2:H*}, there exists a tuple $\bm{t}\in \J(R_1,...,R_{k-3}, H', V)$ satisfying $\bm{t}[k-2] = h'$ and $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$}$ (recall that $\bm{t}[k-1]$ is a vertical segment). We map $h^*$ to $\bm{t}$.

@@

Next, we will prove that a rectangle $r_{k-2} \in \contained_{R_{k-2}}(h^*)$ if and only if $r_{k-2} \in \contained_{R_{k-2}}(\bm{t})$. According to the definitions of $\contained_{R_{k-2}}(h^*)$ and $\contained_{R_{k-2}}(\bm{t})$ --- see \eqref{eqn:contained} and \eqref{eqn:type2:contained-t}, respectively --- it suffices to show that $h^*$ is the same as the effective horizontal segment of $\bm{t}$. Denote by $x$ the x-coordinate of the vertical segment $\bm{t}[k-1]$. Then, the point $h' \cap v$ (intersection between $h'$ and $v$) is $(x,y)$, where as mentioned $y$ is the y-coordinate of $h'$. The effective horizontal segment of $\bm{t}$ is therefore $[x_1,x]\times y$. Recall that $h^* = [x_1,\minleft(h')]\times y$, where $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$} = x$. Therefore, $h^*$ is the same as the effective horizontal segment of $\bm{t}$.

@@

It remains to show that no two distinct segments $h_1^*, h_2^* \in H^*$ can be mapped to the same tuple in $\J(R_1,...,R_{k-3}, H',V)$. Assume, on the contrary, that $h_1^*$ and $h_2^*$ are mapped to the same tuple $\bm{t}\in \J(R_1,...,R_{k-3}, H',V)$. Suppose that $h_1^*$ (resp., $h_2^*$) is the minimal segment of $h_1'$ (resp., $h_2'$). Under our mapping, it must be true that  $h_1' = h_2' = \bm{t}[k-2]$. However, the distinctness of $h_1^*$ and $h_2^*$ requires $h_1' \ne h_2'$, which yields a contradiction.

@@

%Then, $B_\bm{t}$, which is the intersection of $h'$ and $v$, is $(x,y)$.

>>>>

\extraspacing \underline{\em Proof of Statement (1).} We will map each segment $h^* \in H^*$ to a unique tuple $\bm{t}\in \J(R_1,...,R_{k-3},H',V)$ satisfying $\contained_{R_{k-2}}(h^*) = \contained_{R_{k-2}}(\bm{t})$. The mapping allows us to derive
\myeqn{
    \sum_{h^* \in H^*} |\contained_{R_{k-2}}(h^*)|
    \le
    \sum_{\bm{t} \in \J(R_1,...,R_{k-3},H',V)} |\contained_{R_{k-2}}(\bm{t})|
    \leq \out \nn
}
where the last inequality used Statement (3) of Lemma~\ref{lmm:hv:type2:properties}.

@@

The mapping is as follows. Consider any $h^* \in H^*$. Recall that $h^*$ is the minimal segment of some segment $h' \in H'$. Specifically, if $h' = [x_1,x_2]\times y$, then $h^* = [x_1,\minleft(h')]\times y$. By the definition of $\minleft(h')$ in \eqref{eqn:hv:type2:H*}, there exists a tuple $\bm{t}\in \J(R_1,...,R_{k-3}, H', V)$ satisfying $\bm{t}[k-2] = h'$ and $\minleft(h') = \text{$x$-coordinate of the vertical segment $\bm{t}[k-1]$}$. We map $h^*$ to $\bm{t}$.

@@

Next, we will prove
\begin{center}
    {\bf Claim 1:} a rectangle $r \in \contained_{R_{k-2}}(h^*)$ if and only if $r \in \contained_{R_{k-2}}(\bm{t})$.
\end{center}
According to the definitions of $\contained_{R_{k-2}}(h^*)$ and $\contained_{R_{k-2}}(\bm{t})$ --- see \eqref{eqn:contained} and \eqref{eqn:type2:contained-t}, respectively --- it suffices to show that $h^*$ is the same as the effective horizontal segment of $\bm{t}$.

@@

Denote by $x$ the x-coordinate of $\bm{t}[k-1]$. Then, the point $h' \cap v$ can be written as $(x,y)$, where as mentioned $y$ is the y-coordinate of $h'$. The effective horizontal segment of $\bm{t}$ is therefore $[x_1,x]\times y$. Recall that $h^* = [x_1,\minleft(h')]\times y$, where (by definition of $\bm{t}$) $\minleft(h') = \text{$x$-coordinate of $\bm{t}[k-1]$} = x$. Therefore, $h^*$ is the same as the effective horizontal segment of $\bm{t}$, proving claim 1.

It remains to show that no two distinct segments $h_1^*, h_2^* \in H^*$ can be mapped to the same tuple in $\J(R_1,...,R_{k-3}, H',V)$. Assume, on the contrary, that $h_1^*$ and $h_2^*$ are both mapped to $\bm{t}\in \J(R_1,...,R_{k-3}, H',V)$. Suppose that $h_1^*$ (resp., $h_2^*$) is the minimal segment of $h_1'$ (resp., $h_2'$). Under our mapping, it must hold that  $h_1' = h_2' = \bm{t}[k-2]$. However, the distinctness of $h_1^*$ and $h_2^*$ requires $h_1' \ne h_2'$, which yields a contradiction.

@@
